predict

### 2020-11-02 predict.Rmd
more stuff
more stuffs

```{r}
cell_counts <- readRDS("inputs/cell_counts.RDS")
model <- readRDS("model/4chains_3000iter_.rds")
```

@@

```{r}
overall_prop$predict <- predict(model, type = "response", newdata = overall_prop)[,1]
nrow(overall_prop$predict)
```

```{r}
overall_prop$vote <- ifelse(overall_prop$predict >0.5, 1, 0)
```

```{r}
overall_prop$vote_weight <- overall_prop$vote * overall_prop$prop

@@

```{r}
head(overall_prop$vote_weight)

>>>>

```{r}
#load in counts for each demographic
cell_counts <- readRDS("inputs/cell_counts.RDS")
#load in a pre-trained model, more models can be found in models folder
#models can be trained in the build-Model.R file
model <- readRDS("model/4chains_3000iter_.rds")
```

@@

```{r}
#apply model on the post stratification data set
overall_prop$predict <- predict(model, type = "response", newdata = overall_prop)

overall_prop$vote_biden <- if_else(overall_prop$predict[,1] > 0.5, 1, 0)
```

```{r}
overall_prop$vote_weight <- overall_prop$vote_biden * overall_prop$prop

@@

```{r}
saveRDS(overall_prop, file='processed_data/predictions.RDS')
```

```{r}
biden <-sum(overall_prop$vote_weight)
trump <- 1 - biden
```
